---
title: "R Notebook"
output: html_notebook
---

运行：按钮 / *Cmd+Shift+Enter*.

```{r}
plot(cars)
```

插入一行代码块：按钮 / *Cmd+Option+I*.

## matrix() 新建一个矩阵

```{r}
vector <- c(1, 2, 3, 4) 
nameRow = c("row1", "row2")
nameCol = c("col1", "col2")
mymatrix <- matrix(vector, 2, 2, TRUE, dimnames = list(nameRow, nameCol))  # matrix(data, ncol, nrow, byrow);
print(mymatrix)
```

difference between `byrow = FALSE` and `byrow = TRUE`

-   `TRUE`: 1 3 2 4

-   `FALSE`: 1 2 3 4

### get value of a matrix

```{r}
mymatrix
mymatrix[2,2]
mymatrix[1,1:2]
```

## Dataframes

```{r}
d <- c(1, 2, 3, 4)
e <- c(TRUE, TRUE, TRUE, FALSE)
f <- c("red", "white", "red", NA)
mydata <- data.frame(d, e, f)     # 所有向量行数必须相等
names(mydata) <- c("ID", "Passed", "Color")
print(mydata)
```

-   `names()` 设置列名称

-   `data.frames()` 中所有向量的行数必须相等；

```{r}
mydata[1:2]
mydata[c("ID", "Passed")]
mydata$ID
```

## List 列表

an **ordered** collection of objects.

```{r}
w <- list(name = "student 1", q1 = c(1:2), math = "GOOD")
v <- list(name = "student 2", english = 60, math = 90)
rsl = list(w, v)
rsl
```

## Input and Processing

### import data

```{r}
mydata <- read.csv("", header = TRUE, sep = ",")
```

### export data

```{r}
write.table(mydata, "", sep = "\t")
```

## Viewing Data

```{r}
ls()
names(mydata)
str(mydata)
dim(mydata)
```

```{r}
class(mydata)
mydata
head(mydata, n = 2)
tail(mydata, n = 1)
```

-   `class(object)` class of a object

<!-- -->

-   `head(object, n)` print first 2 row of data

-   `tail(object, n)` print last 1 row of data

## missing data
